Job Demands-Resources Model Components through the Lens of O*NET Classifications

### 2023-03-02 Submission.Rmd
updated RQ explanations again.

In addition to the two hypotheses, two related research questions were proposed: 1) do literature-implicated resources materialize as perceived resources and 2) do literature-implicated demands materialize as perceived demands? To answer these questions, authors first categorized O\*Net items into the JD-R elements listed in the JD-R literature. For example, autonomy is frequently described as a resource in the JD-R literature. An O\*Net item in the autonomy category is, “How much decision making freedom, without supervision, does your job offer?”. This O\*Net item was therefore retained within the "autonomy" category. Mean ratings (of resource, challenge, and hindrances) were then computed to explore whether literature-implicated resources and demands were evaluated as such.

Repeated-measures ANOVAs were computed for the group of literature-implicated *resources* (see the right hand side of Figure 4). The effect for `Job Control` was $F_{(`r report7$ANOVA$DFn`, `r report7$ANOVA$DFd`)}$ = `r report7$ANOVA$F` ($\eta^2$ = `r report7$ANOVA$pes`).
The effect for `Participation` was $F_{(`r report8$ANOVA$DFn`, `r report8$ANOVA$DFd`)}$ = `r report8$ANOVA$F` ($\eta^2$ = `r report8$ANOVA$pes`).
The effect for `Autonomy` was $F_{(`r report9$ANOVA$DFn`, `r report9$ANOVA$DFd`)}$ = `r report9$ANOVA$F` ($\eta^2$ = `r report9$ANOVA$pes`).
The effect for `Team Cohesion` was $F_{(`r report10$ANOVA$DFn`, `r report10$ANOVA$DFd`)}$ = `r report10$ANOVA$F` ($\eta^2$ = `r report10$ANOVA$pes`).Statistical significance was less then .001 for all four category comparisons. Here, the pattern was as expected. Across categories, resources were rated the highest (see white bars representing resources in Figure 4). However, as can be seen, mean challenge (which is a demand) was rated quite similarly and above the midpoint of 3 across JD-R categories.

Next, repeated-measures ANOVAs were then run for the group of literature-implicated *demands*.  The effect for `Overwork` was $F_{(`r report1$ANOVA$DFn`, `r report1$ANOVA$DFd`)}$ = `r report1$ANOVA$F`, partial eta squared $(\eta^2)$ was `r report1$ANOVA$pes`. The effect for `Physical Environment` was $F_{(`r report2$ANOVA$DFn`, `r report2$ANOVA$DFd`)}$ = `r report2$ANOVA$F` ($\eta^2$ = `r report2$ANOVA$pes`). The effect for `Time Pressure` was $F_{(`r report3$ANOVA$DFn`, `r report3$ANOVA$DFd`)}$ = `r report3$ANOVA$F` ($\eta^2$ = `r report3$ANOVA$pes`). The effect for `Emotional Demands` was $F_{(`r report4$ANOVA$DFn`, `r report4$ANOVA$DFd`)}$ = `r report4$ANOVA$F` ($\eta^2$ = `r report4$ANOVA$pes`).
The effect for `Recipient Contact` was $F_{(`r report5$ANOVA$DFn`, `r report5$ANOVA$DFd`)}$ = `r report5$ANOVA$F` ($\eta^2$ = `r report5$ANOVA$pes`). The effect for `Work Pressure` was $F_{(`r report6$ANOVA$DFn`, `r report6$ANOVA$DFd`)}$ = `r report6$ANOVA$F` ($\eta^2$ = `r report6$ANOVA$pes`). In all cases, statistical significance was less then .001, indicating that what the literature implicates is a demand was actually rated as a resource (all resource means are above the midpoint). This is contrary to the expectation that ratings would match our assumption of what a resource constitutes. Looking at demands, there is a large difference between whether a characteristic is viewed as a challenge or hindrance.See the pattern of white resource bars on the lefthand side of Figure 4.

>>>>

In addition to the two hypotheses, two related research questions were proposed: 1) do literature-implicated resources materialize as perceived resources and 2) do literature-implicated demands materialize as perceived demands? To answer these questions, authors first categorized O\*Net items into the JD-R elements listed in the JD-R literature. For example, autonomy is frequently described as a resource in the JD-R literature. An O\*Net item in the autonomy category is, “How much decision making freedom, without supervision, does your job offer?”. This O\*Net item was therefore retained within the "autonomy" category. Mean ratings of the O\*Net items were then computed by element (e.g., all of the items representing autonomy) to explore whether literature-implicated resources and demands were evaluated as such.

Repeated-measures ANOVAs were computed for the group of literature-implicated *resources* first (see the right hand side of Figure 4). The effect for `Job Control` was $F_{(`r report7$ANOVA$DFn`, `r report7$ANOVA$DFd`)}$ = `r report7$ANOVA$F` ($\eta^2$ = `r report7$ANOVA$pes`).
The effect for `Participation` was $F_{(`r report8$ANOVA$DFn`, `r report8$ANOVA$DFd`)}$ = `r report8$ANOVA$F` ($\eta^2$ = `r report8$ANOVA$pes`).
The effect for `Autonomy` was $F_{(`r report9$ANOVA$DFn`, `r report9$ANOVA$DFd`)}$ = `r report9$ANOVA$F` ($\eta^2$ = `r report9$ANOVA$pes`).
The effect for `Team Cohesion` was $F_{(`r report10$ANOVA$DFn`, `r report10$ANOVA$DFd`)}$ = `r report10$ANOVA$F` ($\eta^2$ = `r report10$ANOVA$pes`).Statistical significance was less then .001 for all four category comparisons. Here, the pattern was as expected. Across categories, resources were rated the highest (see white bars representing resources in Figure 4). However, as can be seen, mean challenge (which is a demand) was rated quite similarly and above the midpoint of 3 across JD-R categories.

Next, repeated-measures ANOVAs were then run for the group of literature-implicated *demands*. See the left hand side of Figure 4. The effect for `Overwork` was $F_{(`r report1$ANOVA$DFn`, `r report1$ANOVA$DFd`)}$ = `r report1$ANOVA$F`, partial eta squared $(\eta^2)$ was `r report1$ANOVA$pes`. The effect for `Physical Environment` was $F_{(`r report2$ANOVA$DFn`, `r report2$ANOVA$DFd`)}$ = `r report2$ANOVA$F` ($\eta^2$ = `r report2$ANOVA$pes`). The effect for `Time Pressure` was $F_{(`r report3$ANOVA$DFn`, `r report3$ANOVA$DFd`)}$ = `r report3$ANOVA$F` ($\eta^2$ = `r report3$ANOVA$pes`). The effect for `Emotional Demands` was $F_{(`r report4$ANOVA$DFn`, `r report4$ANOVA$DFd`)}$ = `r report4$ANOVA$F` ($\eta^2$ = `r report4$ANOVA$pes`).
The effect for `Recipient Contact` was $F_{(`r report5$ANOVA$DFn`, `r report5$ANOVA$DFd`)}$ = `r report5$ANOVA$F` ($\eta^2$ = `r report5$ANOVA$pes`). The effect for `Work Pressure` was $F_{(`r report6$ANOVA$DFn`, `r report6$ANOVA$DFd`)}$ = `r report6$ANOVA$F` ($\eta^2$ = `r report6$ANOVA$pes`). In all cases, statistical significance was less then .001. However, the findings revealed that what the literature implicates as a demand was actually evaluated as a *resource* (all resource means are above the midpoint). This is contrary to the expectation that ratings would match our assumption of what a demand constitutes. Looking at demands, there is a large difference between whether a characteristic is viewed as a challenge or hindrance. See the pattern of white resource bars on the lefthand side of Figure 4.
